Lasso_RCI_Response

### 2024-02-21 Lasso_RCI_Response.Rmd
Created table one

library(JTRCI)
# library(ClinicalSig)
# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
#Demographics Table
Demo_tab_df <- Mothership_post |>
  #Mothership_Diag_treat |>
  filter(!is.na(Education_1),
         !is.na(Race_1),
         !is.na(Gender_1),
         !is.na(Disorder_Type),
         !is.na(Relationship_1),
         !is.na(RESPONDER_FIGS)
        )

#Demographic tab
Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Demo_tab

Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
Simple_Demo_tab
```

### Treatment information
Overal look at treatment varaibles by treatment response
```{r}
# PHP Treatment information
resp_tab <- data.frame(table1::table1(
   ~ DC_status_1 + IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab
```

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

old model
# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,

@@

Create test and train data - Depression
```{r}
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_dep$Depression_Responder %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_dep[training.samples, ]
test.data <- Vars_dep[-training.samples, ]

@@

# Fit the final model on the training data
model <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                lambda = cv.lasso.dep$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

@@

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)

@@

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        Married + Days_not_attended_1 + Mood_D + Substance_D + Anxiety_C +
        Substance_C + CUDOS_pre + CUXOS_pre + rdq_coping_change + 
        rdq_pmh_change + rdq_func_change,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

## 1se model
  glm_1se_dep <-  
      glm(
      #Outcome varaible
        Depression_Responder ~ 
      # predictors
        rdq_coping_change + rdq_pmh_change + rdq_func_change + rdq_wbs_change,
      #data
      data = Vars_dep, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.dep      <- summary(glm_1se_dep)

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdq_coping_change:rdq_wbs_change
  ))

Vars_anx <- na.omit(Vars_anx)
```

@@

# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso.anx$lambda.min)
# Display regression coefficients
coef(model)
# Make predictions on the test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
mean(predicted.classes == observed.classes)

@@

# Make predictions
probabilities <- full.model %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.full.model.anx <- mean(predicted.classes == observed.classes)

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
         CUXOS_pre + rdq_coping_change + rdq_pmh_change + rdq_func_change,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.anx      <- summary(glm_1se_anx)

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx$type = c("Anxiety")
```

>>>>

library(JTRCI)
citation("JTRCI")

# 
# #devtools::install_github("zieglema/ClinicalSig")
#1. Create df for RCI
RCI_df_dep <- Mothership_post |>
  mutate(
    ID1  = as.integer(ID1),
    pre  = as.numeric(CUDOS_pre),
    post = as.numeric(CUDOS_post),
    Disorder = Disorder_treat
  ) |>
  select(
    ID1,pre,post,Disorder
  ) |>
  filter(!is.na(pre),
         !is.na(post),
         pre > 20)

@@

### Demographics information
- Table 1 Demographics By Response
- Table 2: Treatment information - What did treatment look like?
- Table 3: Scores on measures pre post change? 
    + I want to show the figure of pre-post change???
- Table 4: demographic breakdown
```{r}
# #Demographics Table
# Demo_tab_df <- Mothership_post |>
#   #Mothership_Diag_treat |>
#   filter(!is.na(Education_1),
#          !is.na(Race_1),
#          !is.na(Gender_1),
#          !is.na(Disorder_Type),
#          !is.na(Relationship_1),
#          !is.na(RESPONDER_FIGS)
#         )

# #Demographic tab
# Demo_tab<-data.frame(table1::table1(~Age_1+Race_1+Education_1+Gender_1+Relationship_1 | RESPONDER_FIGS, data=Demo_tab_df))
# colnames(Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
# Demo_tab
# 
# Simple_Demo_tab <-data.frame(table1::table1(~Age_1 + White +IPT_track_1 + Straight + Married + Female +  Some_College + Discharge | RESPONDER_FIGS, data=Demo_tab_df))
# colnames(Simple_Demo_tab) <- c("Demographic","Non-Responder", "Responder","Total Sample")
# Simple_Demo_tab
# 
# Table

library(tableone)

### first gather information based upon anxiety

## Vector of variables to summarize
table1_vars_anx <- c(colnames(Vars_anx)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_anx <- CreateTableOne(vars = table1_vars_anx, data = Vars_anx,strata ="Anxiety_Responder",  factorVars = catVars)
table1_tab_anx <- print(table1_tab_anx, formatOptions = list(big.mark = ","))
tab1_df_anx <- data.frame(table1_tab_anx)

### next gather info based upon depression

## Vector of variables to summarize
table1_vars_dep <- c(colnames(Vars_dep)[-1])

## Vector of categorical variables that need transformation
catVars <- c("Some_College", "Female" , "Married", "White",
             "IPT_track_1","Anxiety_D", "Mood_D", "BPD_P" ,"Trauma_D","Substance_D" ,        
             "Psychotic_D", "Other", "Anxiety_C", "Mood_C" , "BPD_Co_C", "Trauma_C", 
             "Substance_C", "Other_C" , "No_Co"
             )
## Create a TableOne object
table1_tab_dep <- CreateTableOne(vars = table1_vars_dep, data = Vars_dep,strata ="Depression_Responder",  factorVars = catVars)
table1_tab_dep <- print(table1_tab_dep, formatOptions = list(big.mark = ","))
table1_tab_dep <-data.frame(table1_tab_dep)
table1_tab_dep

## lastly get the overal treatment breakdown
table1_gen <- CreateTableOne(vars = table1_vars_dep, data = Mothership_lasso_anx,  factorVars = catVars)
table1_gen <- print(table1_gen, formatOptions = list(big.mark = ","))
table1_gen <-data.frame(table1_gen)
table1_gen 
```

### Treatment information
Overal look at treatment varaibles by treatment response
```{r}
# PHP Treatment information
resp_tab <- data.frame(table1::table1(
   ~IPT_track_1 + Days_complete_1 + Days_cancel_1 + Days_not_attended_1 + Days_noshow_1 | RESPONDER_FIGS, 
  data = Mothership_post))
colnames(resp_tab) <- c("Variable","Non-Responder", "Responder", "Total Sample")
resp_tab
```

@@

Vars_dep <- Mothership_lasso_dep |>
  select( c(
    Depression_Responder,
    # Demographics
    Age_1,Some_College:Married,White, 
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, 
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre,
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

# old model
# Anxiety_D, Mood_D, BPD_P,    Trauma_D,  Other,
#     Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
#     Current_Dx,

@@

Create test and train data - Depression
```{r}
library(glmnet)
library(caret)
# Create Training and testing data
set.seed(123) 
training.samples <- Vars_dep$Depression_Responder %>% 
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- Vars_dep[training.samples, ]
test.data <- Vars_dep[-training.samples, ]

@@

# Fit the final model on the training data
model.min <- glmnet(x.dep, y.dep, alpha = 1, family = "binomial",
                lambda = cv.lasso.dep$lambda.min)
# Display regression coefficients
coef(model.min)

# Make predictions on the test data
x.test <- model.matrix(Depression_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
mean(predicted.classes == observed.classes)

@@

# Make predictions
probabilities <- full.model.dep %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Depression_Responder
Mean.predict.full.model.dep <- mean(predicted.classes == observed.classes)

@@

```{r}
## min model
  glm_min_dep <-
      glm(
      #Outcome varaible
        Depression_Responder ~
      # predictors
        White + Days_complete_1 + Days_not_attended_1 + Mood_D + Substance_D + 
        Other + Anxiety_C + Mood_C + Substance_C + CUDOS_pre + CUXOS_pre + 
        rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + rdqPOST_wbs,
      #data
        data = Vars_dep,
      # type of regression : logistic = binary / binomial
        family = "binomial")

@@

## 1se model
  glm_1se_dep <-  
      glm(
      #Outcome varaible
        Depression_Responder ~ 
      # predictors
        Days_not_attended_1+ rdqPOST_coping + rdqPOST_pmh + rdqPOST_func + 
        rdqPOST_wbs,
      #data
      data = Vars_dep, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.dep      <- summary(glm_1se_dep)

@@

Vars_anx <- Mothership_lasso_anx |>
  select( c(
    Anxiety_Responder,
    # Demographics
    Age_1,Some_College:Married,White, #Discharge,
    # Treatment info
    IPT_track_1, Days_complete_1, Days_not_attended_1, #Days_cancel_1,
    # Disorders
    Anxiety_D, Mood_D, BPD_P,    Trauma_D, Substance_D, Psychotic_D,  Other,
    Anxiety_C, Mood_C, BPD_Co_C, Trauma_C, Substance_C, Other_C, No_Co,
    Current_Dx,
    # Pre-Post stuff
    CUDOS_pre,CUXOS_pre, #CUDOS_first,CUXOS_first
    # RDQ
    rdqPOST_coping:rdqPOST_wbs
  ))

Vars_anx <- na.omit(Vars_anx)

citation("glmnet")
```

@@

# Fit the final model on the training data
model <- glmnet(x, y, alpha = 1, family = "binomial",
                lambda = cv.lasso.anx$lambda.min)
# Display regression coefficients
# coef(model)
# Make predictions on the test data
x.test <- model.matrix(Anxiety_Responder ~., test.data)[,-1]
probabilities <- model %>% predict(newx = x.test)
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
mean(predicted.classes == observed.classes)

@@

# Make predictions
probabilities <- full.model.anx %>% predict(test.data, type = "response")
predicted.classes <- ifelse(probabilities > 0.5, "Responder", "Non-Responder")
# Model accuracy
observed.classes <- test.data$Anxiety_Responder
Mean.predict.full.model.anx <- mean(predicted.classes == observed.classes)

@@

## 1se model
  glm_1se_anx <-  
      glm(
      #Outcome varaible
        Anxiety_Responder ~ 
      # predictors
        Days_not_attended_1 + CUXOS_pre + rdqPOST_coping + rdqPOST_pmh + rdqPOST_wbs,
      #data
      data = Vars_anx, 
      # type of regression : logistic = binary / binomial
      family = "binomial")
# Summary of the model
  summary.1se.anx      <- summary(glm_1se_anx)

@@

# Left join the FDR adjusted p.value
FP.1se.anx <- left_join(FP.1se.anx,ADJ.p.values.1se.anx, by = join_by(p.values == p.value))
FP.1se.anx$type = c("Anxiety")
FP.1se.anx
```
